---
title: "Unsupervised ML"
author: "Shashwat Patel"
date: "04/02/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message = FALSE)
```

# Attaching the required packages

```{r}
library(tidyverse)
library(factoextra)

```

# Read the data

```{r}
data<-read.csv("Iris.csv")
head(data)
```

# Basic summary of the data. 

```{r}
summary(data)
```

### **Removing non-numeric categories from the data**

```{r}
species<-data$Species
data<-data[,c(-1,-6)]
head(iris)
```

### **Elbow method to find opimal value of k or number of clusters**

- It can be clearly seen that optimal number of cluster is 3, as the value of Total Within sum of square remains neraly the same after k=3.

```{r}
fviz_nbclust(data,FUNcluster = kmeans,method="wss") 
```

# K-means clustering

```{r}
k_mean<-kmeans(x=data,centers=3,nstart = 25)
k_mean
```

# Cluster Plot

- This function uses principle componet analysis for dimensional reduction.

```{r}
fviz_cluster(k_mean,data=data)+ scale_fill_discrete(labels=c("Iris-Setosa","Iris-Versicolor","Iris-Virginica"))
```

### Adding cluster label to the dataset

```{r}
clustered_data<-data.frame(Species=species,Cluster_no=k_mean$cluster)
head(clustered_data)
```

- Full data available now.
 
```{r}
full_data<-cbind(data,clustered_data)
full_data$Cluster_no<-factor(full_data$Cluster_no)
head(full_data)
```

# Centroid values

```{r}
centers<-k_mean$centers
centers<-as.data.frame(centers)
centers

```

# Plot containig the clusters as well  as the centroid positions.

- The centroids are in black colour.



```{r}
full_data%>%ggplot()+geom_point(aes(x =SepalLengthCm,y=SepalWidthCm,colour=Cluster_no))+geom_text(aes(x=5,y=4),label="Iris-Setosa",size=3,colour="red")+
                                                  geom_text(aes(x=5.5,y=2.5),label="Iris-virginica",colour="blue",size=3)+
geom_text(aes(x=7,y=3.4),label="Iris-versicolor",colour="darkgreen",size=3)+
geom_point(data=centers,aes(x=SepalLengthCm,y=SepalWidthCm))  
```


### This concludes the task-2
